Density-dependent selection and the limits of relative fitness

### 2018-04-26 manuscript.tex
l

The above findings underscore that the most serious threat to the density-independent models of selection (Eqs.~\eqref{eq:canonicalcont} and \eqref{eq:canonicalcont}) arises due to deviations from demographic equilibrium as a result of changes in the demographic rates of the types already present i.e. as a result of a temporally-variable environment. While transient deviations from demographic equilibrium driven by the appearance of new types can also threaten the density-independent approximation, this requires strong selection that is both density-dependent and affects a density-regulating trait (and, as exemplified by $b$-selection, even then the approximation may hold). By contrast, temporally-variable environments can dramatically alter frequency trajectories for individual sweeps (e.g. Fig. 9.5 in \cite{otto_2011}; Fig. 5 in \cite{mallet_2012}), as well as the long-term outcomes of selection \citep{lande_2009}.

>>>>

The above findings underscore that the most serious threat to the density-independent models of selection (Eqs.~\eqref{eq:canonicalcont} and \eqref{eq:canonicaldisc}) arises due to deviations from demographic equilibrium as a result of changes in the demographic rates of the types already present i.e. as a result of a temporally-variable environment. While transient deviations from demographic equilibrium driven by the appearance of new types can also threaten the density-independent approximation, this requires strong selection that is both density-dependent and affects a density-regulating trait (and, as exemplified by $b$-selection, even then the approximation may hold). By contrast, temporally-variable environments can dramatically alter frequency trajectories for individual sweeps (e.g. Fig. 9.5 in \cite{otto_2011}; Fig. 5 in \cite{mallet_2012}), as well as the long-term outcomes of selection \citep{lande_2009}.
